\chapter{Introduction}

As of writing this report the IP/TCP protocol which functions as a back bone of the internet was first demonstrated exactly 40 years ago.
The HTTP protocol which we use to transfer web application was created shortly after.
Throughout those 40 years the the web landscape has change multiple times.
Currently every single service imaginable can be accessed online, from banking, through education, to entertainment.
Everybody across the globe has grown used to the vast possibilities that the internet provides.

With all the positive impact of the internet there are also risks.
As all our data has at some point been exposed to the World Wide Web, there have appeared bad actors who are interested in collecting and abusing our information.
A common way of extorting information is to access it directly in the users browser.
Old reports claiming that 65\% of websites are vulnerable to Cross Site Scripting(XSS) attacks \cite{xssEverywhere} and newer reports showing that almost 40\% of all attacks are performed using XSS \cite{xssEverywhere2}.
Hacker one, one of the companies that unites ethical hackers and provides other security services, ranks XSS as the most rewarded vulnerability \cite{xssMoney}.

This report, after a brief introduction to cross site scripting and content security polices(CSP), presents a fresh and innovative approach to detect ongoing attacks.
After detailing the inner workings of the newly designed system, it is tested by simulating real world scenarios which use currently accessible websites.
After the results are collected, the paper concludes with a discussion on many third party issues that were encountered throughout the development which if resolved could increase either security or performance of the final product.



